Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-22 paper/paper.tex
pass on results

Table~\ref{tab:cross-testing} shows the number of failures observed
for each pair of test suite and engine. The first column shows the
test suites and the first row shows the engines that run those
tests. We use a dash (``-'') to indicate that we did not consider the
combinations that associate a test suite with its parent engine;
failures in those cases would either indicate regressions or flaky
tests as opposed to unknown bugs for that engine. We did not run test
cases that fail on its parent engine in any other engines; we wanted
all tests to pass on their parent engine as that would indicate that
the test case is coherent and can be used. In total, 64 test cases
were discarded for that reason--6 from \jsc{} and 57 from
\smonkey. Furthermore, we required that a test does not manifest
compile errors as we want to focus on bugs in code not in tests. For
that reason, we used the tests listed under the column
``compile-in-all'' from Table~\ref{tab:test-suites}, totalling
\totalTestFilesCompileInAll{} cases. \Mar{can you confirm that we used
  ``compile-in-all'' and not ``origina'' as these numbers
  suggest?}\Fix{In total, 7,029 test files (\ie{}, 38369-31276-64)
  were considered in this experiment, which involved 24,922 test runs
  (\ie, (7029*4)-1021-57-2116).}  Of these, 812 failures were observed
(3.25\% of the runs) across \textbf{543} distinct files (7.72\% of the
files). We analyzed each of these files in separate as to classify if
the failure was fault-revealing or a false positive.

\Mar{-------------------- estou aqui}

We observed from the table that, considering this dataset, the Mozilla
\smonkey\ was the engine that failed the least whereas the Microsoft
engine \chakra\ failed the most. The \smonkey\ test suite also
revealed more failures than any other, perhaps as expected,
considering that it is the suite with more tests (see
Table~\ref{tab:test-suites}).

@@

The piecharts from Figure~\ref{fig:piecharts-transplantation} show the
false and true positives observed with test transplantation. The top
piechart shows false alarms, which means that all
``transplanted'' tests should have passed in these cases. The absolute
number of tests in each category is shown in parentheses to the
right-side of each slice label, naming the source of false
positive. The sources are as follows:

@@

  \item \textbf{Timeout/OME\footnote{ome is for out of memory
      error.}.} False positives of this kind manifest because the
    engine that runs the test does not optimize the code as the
    original engine and that has an effect in the test outcome.  The
    test may fail to finish at the time budget or runs out of
    memory. For example, a test case from \jsc{} defines a function
    with a tail-call recursion. The test fails in all engines but
    \jsc{}, which implements tail-call optimization.

    %% \Igor{
    %%   For example, a testcase from \jsc{} suite explores the tail call
    %%   to optimize the recursion, the test uses a recursive function that
    %%   should be executed multiple times (ie. \mcodeid{1e6}). In this case, 
    %%   only the \jsc{} supports tail-call optimization and the testcase 
    %%   passes without failures. Another case can be found in \jerry{} suite
    %%   that uses a repetition statement to concatenate long strings 
    %%   exponentially, causing an out of memory error. The engines used 
    %%   supports the flags to increase memory, however we prefer to use 
    %%   the default engine build.
    %% }

  \item \textbf{Not implemented.} False positives of this kind
    manifest when a test fails because it covers a function that is
    part of the official spec, but is not implemented in the target
    engine. For example, at the time of writing, \chakra{} does not
    implement by default various properties from the \mcodeid{Symbol}
    object. These properties are only available activating ES6
    experimental mode with the flag \CodeIn{-ES6Experimental}.

  \item \textbf{Unknown.} This category corresponds to the cases we
    were unable to confidently diagnose the failure.

  %% \item \textbf{Error message mismatch.} Test fails because it
  %%   compares an error message, which is not portable across
  %%   engines. For example, \Igor{
  %%     a test from the engine \jsc{} uses an assert function called
  %%     \CodeIn{shouldThrow} that expects an specific error message. In this test, 
  %%     all engines throws the Error as expected, however only the message 
  %%     on \jsc{} engine match with the string expected in the test case.
  %%   }
\end{itemize}

We observed that the sources of false positives were relatively
uniformly distributed, with the categories ``Unknown'' and
``Undefined'' holding more representation with \Fix{X and Y} reports,
respectively. Considering the true positives, we found a reasonable
number of duplicate reports, but not enough high to justify attempting
to automate the detection of duplicates. Section~\ref{sec:bugs}
exemplifies cases of false and true positives.

@@

Table~\ref{tab:test-transplantation-bugs} lists all bugs we found
with test transplantation. The first column shows the identifier we
assigned to the bug, column ``Date'' shows the date the bug was
reported in the format ``m/dd'', column ``Engine'' shows the affected
engine, column ``Status'' indicates the status of the bug report at
the time of the writing (\eg{},``New'', ``Rejected'', ``Confirmed'',
''Fixed''), column ``Url'' shows the web address for the corresponding
post in the bug tracking system where the discussion thread with
engine developers can be found (de-anonymized upon request), column
``Severity'' shows the severity level for confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test. Considering severity levels, it is important to note that
\jsc{} uses five different severity levels~\cite{jsc-severity} whereas
\chakra{}~\cite{chakra-severity} and \smonkey{}~\cite{mozilla-severity}
use only two. As usual, the smallest the severity value the highest
the severity of the bug. We use a dash (``-'') as the severity level
for bugs with pending confirmation.

Of the \Fix{17} bugs we reported with test transplantation, \Fix{9}
were analyzed and moved from the status ``New'' to ``Confirmed''
(\ie{}, no bug we reported was rejected). Of these, \Fix{8} of them
are severity-2 bugs.  \chakra{} was the engine with the highest number
of confirmed bugs, \Fix{8} in total, with \Fix{1} bug
fixed. Considering the remaining engines, \veight{} confirmed one
bug. Curiously, Google engineers confirmed that report in a few
hours. Although we did not find any showstopper critical bugs, most of
the bugs are seemingly important as per the categorization given by
engineers. Analyzing the issue tracker of \chakra, we found that
severity-1 bugs are rare.

@@

This section reports the results obtained with differential
testing. More precisely, we report results obtained by fuzzing test
inputs, running those inputs on different engines, and checking the
outcomes with a differential oracle (see Figure~\ref{fig:workflow}).

\subsubsection{Methodology}
The methodology we used to assess the effectiveness of cross-engine
differential testing is as follows. To avoid experimental noise, we
only fuzz test files that pass in all engines. The intuition is that
we wanted to avoid the scenario where fuzzing produces a
fault-revealing input based on a test that was already
fault-revealing. This decision ensures that we can establish
cause-effect relationship between fuzzing and the observation of
discrepancy. Column ``no-fail-in-all'' from
Table~\ref{tab:test-suites} shows that a total of
\totalTestFilesPassInAll\ tests satisfy this restriction.

\vspace{1ex}
\noindent\textbf{Exploratory Phase.} For the first three months of the
study, our inspection process was exploratory.  Our goal in this phase
was to learn the extent to which \lo\ warnings could reveal bugs. We
realized that if we found that the ratio of bugs from \lo\ warnings
was rather low, we could focus our inspection efforts only on
\hi\ warnings. That finding would be important to reduce inspection
cost and guide future developments of this approach. To run this
experiment, we trained eight students in analyzing the warnings that
our infrastructure produces. The students were enrolled in a
graduate-level testing class. We listed warnings in a spreadsheet and
requested students to update an ``owner'' column indicating who was
working on it, but we did not enforce an order on the warnings the
students should inspect. Recall from Section~\ref{sec:clusterization}
that we clustered \lo\ warnings in buckets. For that reason, we only
listed one \lo\ warning per representative class/bucket in the
spreadsheet. First, we explained the possible sources of false alarms
with examples and then we asked the students to use the following
procedure when finding a suspicious warning. Analyze the parts of the
spec related to the problem and, if still suspicious, look for
potential duplicates on the bug tracker of the affected engine using
related keywords. If none was reported, indicate in the spreadsheet
that that warning is potentially fault-revealing. We encouraged
students to use lithium~\cite{lithium} to minimize long test cases;
the tests from the Mozilla suite are often longer than others. Only
after the co-authors checked the potential bugs, a bug report was
filed.

@@

\subsubsection{Results} Table~\ref{tab:summary-lo} shows statistics of \lo\ warnings obtained
when fuzzing inputs with different tools. Column ``\# buckets'' show
the number of buckets associated with ``\lo'' warnings whereas column
``avg. \# files per bucket'' show the average number of files per
bucket. Note that \Fix{...}

\begin{table}[h]
  \centering
  \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
  \begin{tabular}{crr}
    \toprule
    & \# buckets & avg. \# files per bucket \\
    \midrule
    \radamsa{} & \Fix{82} & \Fix{3 (241/82)}\\
    \quickfuzz{} & \Fix{38} & \Fix{2 (87/38)} \\
    \bottomrule
  \end{tabular}
\end{table}

Table~\ref{tab:summary-hi} shows the number of \hi\ warnings reported
per engine. Recall that we did not cluster \hi\ warnings as there was
not clear clustering criteria to use for that. Note that \Fix{...}

\begin{table}[h]
  \centering
  \caption{\label{tab:summary-hi}Number of \hi\ warning
    reports per engine.}
  \begin{tabular}{crrrrr}
    \toprule
    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & 2+\\
    \midrule
    \radamsa{} & 30 & 4 & 121 & 3 & 143\\
    \quickfuzz{} & & & & & \\    
    \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table}[t]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    positives buckets per source.}
  \begin{tabular}{crr}
    \toprule
    & \radamsa\ & \quickfuzz\ \\
    Undefined & 18 & - \\
    Timeout/OME & 23 & - \\
    Not Implemented & 19 & - \\
    Upcoming Feature & - & - \\
    Error Message Mismatch & 3 & - \\    
    Invalid Input & 10 & - \\    
    \bottomrule     
  \end{tabular}
\end{table}

>>>>

Table~\ref{tab:cross-testing} shows the number of failures observed
for each pair of test suite and engine. The first column shows the
test suites and the first row shows the engines that run those
tests. We use a dash (``-'') to indicate that we did not consider the
combinations that associate a test suite with its parent engine;
failures in those cases would either indicate regressions or flaky
tests as opposed to unknown bugs for that engine. We did not run test
cases that fail on its parent engine in any other engines; we wanted
all tests to pass on their parent engine as that would indicate that
the test case is coherent and can be used. In total, 64 test cases
were discarded for that reason--6 from \jsc{} and 57 from
\smonkey. Furthermore, we required that a test does not manifest
compile errors as we want to focus on bugs in code not in tests. For
that reason, we used the tests listed under the column
``compile-in-all'' from Table~\ref{tab:test-suites}, totalling
\totalTestFilesCompileInAll{} cases. \Mar{can you confirm that we used
  ``compile-in-all'' and not ``origina'' as these numbers
  suggest?}\Fix{In total, 7,029 test files (\ie{}, 38369-31276-64)
  were considered in this experiment, which involved 24,922 test runs
  (\ie, (7029*4)-1021-57-2116).}  Of these, 812 failures were
manifested (3.25\% of the runs) across \textbf{543} distinct files
(7.72\% of the files). A developer with experience in \js\ analyzed
each of these files in separate as to classify if the failure was
fault-revealing or not (\ie{}, a false positive).  We observed from
the table that, considering this dataset, the Mozilla \smonkey\ was
the engine that failed the least whereas the Microsoft engine
\chakra\ failed the most. The \smonkey\ test suite also revealed more
failures than any other, as expected, considering that it is the suite
with more tests (see Table~\ref{tab:test-suites}).

@@

The piecharts from Figure~\ref{fig:piecharts-transplantation} show the
distribution of false and true positives in this experiment. The
piechart at the top shows false alarms. The absolute number of tests
in each category is shown in parentheses to the right-side of each
slice label, which names the source of false positive. The sources of
false positives are as follows:

@@

  \item \textbf{Timeout/OME\footnote{ome is for out of memory
      error.}.} False positives of this kind manifest because the
    engine that runs the test does not optimize the code as the
    original engine and that has an effect in the test outcome.  The
    test may fail to finish at the specified time budget or it exceeds
    the memory budget. For example, a test case from the \jsc{} suite
    defines a function with a tail-call recursion. The test fails in
    all engines but \jsc{}, which implements tail-call optimization,
    which enables the test to finish execution fast.

  \item \textbf{Not implemented.} False positives of this kind
    manifest when a test fails because it covers a function that is
    part of the official spec, but is not implemented in the target
    engine yet. For example, at the time of writing, \chakra{} does
    not implement by default various properties from the
    \mcodeid{Symbol} object. These properties are only available
    activating the ES6 experimental mode with the flag
    \CodeIn{-ES6Experimental}.

  \item \textbf{Unknown.} This category includes the cases we were
    unable to confidently diagnose the failure but we suspected it was
    a false alarm.

\end{itemize}

We observed that ``Unknown'' and ``Undefined'' were the most
predominant sources of false positives. Considering true positives, we
found a reasonable number of duplicate reports, but not enough high to
justify attempting to automate the detection of duplicates.

@@

Table~\ref{tab:test-transplantation-bugs} lists all bugs we found
with test transplantation. The first column shows the identifier we
assigned to the bug, column ``Date'' shows the date the bug was
reported in the format ``m/dd'', column ``Engine'' shows the affected
engine, column ``Status'' indicates the status of the bug report at
the time of the writing (\eg{},``New'', ``Rejected'', ``Confirmed'',
''Fixed''), column ``Url'' shows the web address for the
bug report entry in the bug tracking system (de-anonymized upon request), column
``Severity'' shows the severity level for confirmed bugs, and,
finally, column ``Suite'' shows the name of the engine that originated
the test.

Considering severity levels, it is important to note that \jsc{} uses
five levels~\cite{jsc-severity} whereas
\chakra{}~\cite{chakra-severity} and
\smonkey{}~\cite{mozilla-severity} use only two. As usual, the
smallest the severity value the highest the severity of the bug. We
use a dash (``-'') as the severity level for bugs with pending
confirmation.  No bug we reported in this experiment was rejected.  Of
the \Fix{17} bugs we reported in this experiment, \Fix{9} were
analyzed and moved from the status ``New'' to ``Confirmed''. Of these,
\Fix{8} are severity-2 bugs.  \chakra{} was the engine with the
highest number of confirmed bugs, \Fix{8} in total, with \Fix{1} bug
fixed. Considering the remaining engines, \veight{} confirmed one
bug. Curiously, Google engineers confirmed that report in a few
hours. We found that development teams of other engines, specially
\jsc\, took much longer to analyze bug reports as can be observed by
some pending reports from April 2018. Although we did not find any
showstopper critical bugs, most of the bugs are seemingly important as
per the categorization given by engineers. Analyzing the issue tracker
of \chakra, we found that severity-1 bugs are rare.

Overall, we found these results promising given that precision (\ie{}
the ratio of true positives over all reports) needs to take into
account the cost of inspecting the warning~\cite{harman-ohearn-2018};
it took a week for the developer to inspect the set of warnings
entirely. The precision for \jsc\ was \Fix{X\%} (\ie, XX/270), which
seems a low rate, but it took approximately \Fix{x} days to find
\Fix{y} real bugs on this engine. Section~\ref{sec:bugs} show samples
of false and true positives.

@@

This section reports the results obtained with differential
testing. More precisely, we report results obtained by fuzzing test
inputs, running those inputs on different engines, and checking the
outcomes with a differential oracle.  We configured our infrastructure
(see Figure~\ref{fig:workflow}) to produce 20 well-formed fuzzed files
per input file, \ie{}, the number of fuzzing iterations can exceed the
number above as we discard syntactically invalid files.

\subsubsection{Methodology}
The methodology we used to assess effectiveness of this technique is
as follows. To avoid experimental noise, we only fuzz test files that
pass in all engines.  This corresponds to the tests appearing under
the column ``no-fail-in-all'' from Table~\ref{tab:test-suites}--a
total of \totalTestFilesPassInAll\ tests satisfy this restriction.
The intuition is that we wanted to avoid the scenario where fuzzing
produces a fault-revealing input based on a test that was already
revealing failures on some engine. This decision ensures that we can
establish cause-effect relationship between fuzzing and the
observation of discrepancy.

\vspace{1ex}
\noindent\textbf{Exploratory Phase.} For the first three months of the
study, our inspection process was exploratory.  In this phase, we
wanted to learn whether or not black-box fuzzers could reveal real
bugs and how effective \lo\ warnings were relative to
\hi\ warnings. Considering the choice of fuzzers, we did find several
bugs with \radamsa\, but only some with \quickfuzz. The rationale for
studying the the \hi\ and \lo\ warning classification was that if we
found that the ratio of bugs from \lo\ warnings was rather low, we
could focus our inspection efforts only on \hi\ warnings as we
expected the number of warnings to increase dramatically compared to
the previous experiment. That finding would be important to reduce
inspection cost and guide future developments of this approach. To run
this experiment, we trained eight students in analyzing the warnings
that our infrastructure produces. The students were enrolled in a
graduate-level testing class. We listed warnings in a spreadsheet and
requested the students to update an ``owner'' column indicating who
was working on it, but we did not enforce a strict order on the
warnings the students should inspect. Recall from
Section~\ref{sec:clusterization} that we clustered \lo\ warnings in
buckets. For that reason, we only listed one \lo\ warning per
representative class/bucket in the spreadsheet. First, we explained,
through examples, the possible sources of false alarms they could find
and then we asked the students to use the following procedure when
finding a suspicious warning. Analyze the parts of the spec related to
the problem and, if still suspicious, look for potential duplicates on
the bug tracker of the affected engine using related keywords. If none
was reported, indicate in the spreadsheet that that warning is
potentially fault-revealing. We encouraged students to use
lithium~\cite{lithium} to minimize long test cases; the tests from the
Mozilla suite are often longer than others. Only after the co-authors
checked the potential bugs, a bug report was filed. Each student found
at least one bug using this methodology.

@@

\subsubsection{Results} In this section we discuss results obtained
across these two phases of the experiment. Table~\ref{tab:summary-lo}
shows statistics of \lo\ warnings obtained when fuzzing inputs with
different tools. Column ``\# buckets'' shows the number of buckets
associated with ``\lo'' warnings, column ``\# files'' shows the total
number of files involved in these warnings, and column ``avg. \# files
per bucket'' show the average number of files per bucket. Note that
the difference of files per bucket across fuzzers was not very
significant.

\begin{table}[h]
  \centering
  \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
  \begin{tabular}{crrr}
    \toprule
    & \# buckets & \# files & avg. \# files per bucket \\
    \midrule
    \radamsa{} & 82 & 241 & 2.9 \\
    \quickfuzz{} & 38 & 87 & 2.3 \\
    \bottomrule
  \end{tabular}
\end{table}

Table~\ref{tab:summary-hi} shows statistics for \hi\ warnings; recall
from Section~\ref{sec:clusterization} that we do not cluster
\hi\ warnings\Comment{ as there was no clear clustering criteria to
  use for that}. This table breaks down \hi\ warning by the affected
engine, \ie, the engine manifesting a distinct output among those
analyzed. Column ``+1'' show the cases where more than one engine
disagree on the output. Note that the ordering of engines considering
this metric is consistent with the one observed on
Table~\ref{tab:cross-testing}, with \chakra\ and then \jsc\ associated
with more warnings/failures compared to other engines.
%\veight\ and \smonkey.

\begin{table}[h]
  \centering
  \caption{\label{tab:summary-hi}Number of \hi\ warning
    reports per engine.}
  \begin{tabular}{crrrrr}
    \toprule
    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey & +1\\
    \midrule
    \radamsa{} & 30 & 4 & 121 & 3 & 143\\
    \quickfuzz{} & & & & & \\    
    \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table}[h]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    positives buckets per source.}
  \begin{tabular}{crr}
    \toprule
    & \radamsa\ & \quickfuzz\ \\
    Undefined & 18 & - \\
    Timeout/OME & 23 & - \\
    Not Implemented & 19 & - \\
    Upcoming Feature & - & - \\
    Error Message Mismatch & 3 & - \\    
    Invalid Input & 10 & - \\    
    \bottomrule     
  \end{tabular}
\end{table}
